---
title: "Laboratorio #1 George Albadr"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(dplyr)
library(writexl)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


```{r read_and_unify}
modificar <-  function(archives){
  data = read_excel(archives)
  data = select(data, COD_VIAJE, CLIENTE, UBICACION, CANTIDAD, PILOTO, Q, CREDITO, UNIDAD)
  mes = substr(archives, 3, 4)
  ano = substr(archives, 6, 9)
  data$Fecha = paste0(mes, "-", ano)
  return(data)
}
ruta = 'Lab1'
lista = list.files(pattern = "\\.xlsx", full.names = TRUE)
print(lista)
listadf=lapply(lista, modificar)
tabla = bind_rows(listadf)
print(tabla)
write_xlsx(tabla, "tabla.csv")
```
```{r}
# Nueva lista de vectores
lista_vectores <- list(
  c(5, 10, 10, 15, 20, 10, 25),
  c(7, 14, 14, 21, 14, 28, 7),
  c(2, 4, 4, 6, 8, 4, 10)
)

# Función para calcular la moda
calcular_moda <- function(x) {
  tabla_frec <- table(x)
  moda <- as.numeric(names(tabla_frec)[tabla_frec == max(tabla_frec)])
  return(moda)
}

# Aplicar la función a cada vector de la lista
modas <- lapply(lista_vectores, calcular_moda)
print(modas)
```

